Prefetching SPARQL query cacher

### 2016-07-29 dissertation/cache-proxy.tex
some proofreading

The objective of the analyser in Figure~\ref{fig:arch} is to predict
what remote data is most useful to answer future queries. I haven't
attempted to formalise the notion of what a useful cache entry is, nor
have I attempted to exploit the concept of profitable query patterns
of \cite{papailiou2015graph}, mostly because this work came at a time
where my work was already near the deadline. I opted for a simple
approach to consider only individual triple patterns.

@@

It is then assumed that the cost of accessing the cache is usually
lower than the above, i.e. it should usually be below the lowest cost
of a TPF (yet have no upper bound), and is therefore designated as
\begin{equation}
C_c = 2 + \floor{\log_{10}{n_c}} , 
\end{equation}
where $n_c$ is the number of triples in the cache that matches the
given triple pattern.

@@

If the plan is a hash join the, we continue to follow the example of
the Attean implementation and set
\begin{equation}\label{eq:ch}
T_{A \bowtie_{h} B} = 10 ((1 + C_A) + C_B ) .
\end{equation}
Further, if there are no shared variables, the cost of
Eq.~(\ref{eq:ch}) is multiplied by a factor of 100 rather than 10 so
that if it is necessary to evaluate a Cartesian join, it is more
likely done using a nested loop join.

>>>>

The objective of the analyser in Figure~\ref{fig:arch} is to predict
what remote data is most useful to answer future queries. I haven't
attempted to formalise the notion of what a useful cache entry is, nor
have I attempted to exploit the concept of profitable query patterns
of \cite{papailiou2015graph}, mostly because this work came at a time
when my work was already near the deadline. I opted for a simple
approach to consider only individual triple patterns.

@@

I have assumed that the cost of accessing the cache is usually
lower than the above, that is, it should usually be below the lowest cost
of a TPF (yet have no upper bound), and is therefore designated as
\begin{equation}
C_c = 2 + \floor{\log_{10}{n_c}} , 
\end{equation}
where $n_c$ is the number of triples in the cache that matches the
given triple pattern.

@@

If the plan is a hash join, we continue to follow the example of
the Attean implementation and set
\begin{equation}\label{eq:ch}
T_{A \bowtie_{h} B} = 10 ((1 + C_A) + C_B ) .
\end{equation}
Further, if there are no shared variables, the cost of
Eq.~(\ref{eq:ch}) is multiplied by a factor of 100 rather than 10 so
that if it is necessary to evaluate a Cartesian join, it is more
likely done using a nested loop join.
